---
title: "Project Proposal"
author: "STOR 320.01 Group 13"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(corrplot)
```

# Project Roles

- **Creator:** Tianjun Ma
- **Interpreter:** Arul Gundam
- **Orator 1:** Diego Pardo
- **Orator 2:** Ashley Zhang
- **Deliverer:** Yixiao Chen

# Dataset

[Customer Personality Analysis](https://www.kaggle.com/datasets/imakash3011/customer-personality-analysis)
```{r}
Customer <- read.csv("marketing_campaign.csv", sep = "\t")
head(Customer)
Customer
```

# Initial Questions

- **Question 1:** Does online purchase behavior have to do with education level?
```{r}
mod1 = lm(NumWebPurchases ~ Education, data = Customer)
summary(mod1)
plot(jitter(NumWebPurchases, amount = 0.1) ~ factor(Education), data = Customer)
abline(mod1)
```

- **Question 2:** Is there a relationship between the number of children and the amount spent on sweet product?

```{r}
mod2 = lm(MntSweetProducts ~ Kidhome, data = Customer)
summary(mod2)
ggplot(Customer, mapping = aes(x = Kidhome, y = MntSweetProducts)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


- **Question 3:** Is the amount a customer spends on fruit related to the number of children in the customer's household?

```{r}
mod3 = lm(MntFruits ~ Kidhome, data = Customer)
summary(mod3)
ggplot(Customer, mapping = aes(x = Kidhome, y = MntFruits)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


- **Question 4:** Is there a relationship between the customer's yearly household income and the amount spent on gold products?

```{r}
mod4 = lm(MntGoldProds ~ Income, data = Customer)
summary(mod4)
# one outlier has been removed
ggplot(filter(Customer, Income < 200000), mapping = aes(x = Income, y = MntGoldProds)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

- **Question 5:** Is there a relationship between the number of children in a household and the amount spent on wine?

```{r}
mod5 = lm(MntWines ~ Kidhome, data = Customer)
summary(mod5)
ggplot(Customer, mapping = aes(x = Kidhome, y = MntWines)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


- **Question 6:** How does marital status affect the number of store purchases made? 

```{r}
mod6 = lm(NumStorePurchases ~ Marital_Status, data = Customer)
summary(mod6)
anova(mod6)

ggplot(Customer, mapping = aes(x = Marital_Status, y = NumStorePurchases)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

plot(jitter(NumStorePurchases, amount = 0.1) ~ factor(Marital_Status), data = Customer)
abline(mod1)
```

- **Question 7:** From what level of education are customers typically more likely to file a complaint?

```{r}

```

- **Question 8:** Is there a correlation between the number of children in the home and the number of online purchases?

```{r}
mod8 = lm(NumWebPurchases ~ Kidhome, data = Customer)
summary(mod8)
ggplot(Customer, mapping = aes(x = Kidhome, y = jitter(NumWebPurchases, amount = 0.3))) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


- **Question 9:** Is there a relationship between the customer’s age and the amount they spend on wine?

```{r}
# only considered birth after 1900
mod9 = lm(MntWines ~ Year_Birth, data = filter(Customer, Year_Birth > 1900))
summary(mod9)
ggplot(filter(Customer, Year_Birth > 1900), mapping = aes(x = Year_Birth, y = MntWines)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

- **Question 10:** Does buying a certain product correlate to buying another specific product?

```{r}
product_cor = cor(Customer[, c("MntWines", "MntFruits", "MntMeatProducts", "MntFishProducts", "MntSweetProducts", "MntGoldProds")])
product_cor_df <- as.data.frame(product_cor)
product_cor_df
corrplot(product_cor, method = "color")
```





```{r}
ggplot(Customer, mapping = aes(y = MntMeatProducts)) +
  geom_point(aes(x = jitter(Teenhome, amount = 0.1)), size = 0.5) +
  geom_smooth(aes(x = jitter(Teenhome, amount = 0.1)), method = "lm", se = FALSE) +
  geom_point(aes(x = jitter(Kidhome, amount = 0.1)), size = 0.5) +
  geom_smooth(aes(x = jitter(Kidhome, amount = 0.1)), method = "lm", se = FALSE)
```











```{r}
library(ggplot2)
library(ggpubr)

ggplot(data = Customer, aes(x = factor(Kidhome))) +
  geom_boxplot(aes(y = MntWines, color = "Wines"), size = 0.5) +
  geom_boxplot(aes(y = MntFruits, color = "Fruits"), size = 0.5) +
  geom_boxplot(aes(y = MntMeatProducts, color = "Meat"), size = 0.5) +
  geom_boxplot(aes(y = MntFishProducts, color = "Fish"), size = 0.5) +
  geom_boxplot(aes(y = MntSweetProducts, color = "Sweet"), size = 0.5) +
  geom_boxplot(aes(y = MntGoldProds, color = "Gold"), size = 0.5) +
  labs(x = "Number of Children in Household", y = "Amount Spent on Products") +
  guides(color = guide_legend(title = "Products")) +
  stat_regline_equation(aes(x = factor(Kidhome), y = MntWines, color = "Wines"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~") +
  stat_regline_equation(aes(x = factor(Kidhome), y = MntFruits, color = "Fruits"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~") +
  stat_regline_equation(aes(x = factor(Kidhome), y = MntMeatProducts, color = "Meat"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~")+
  stat_regline_equation(aes(x = factor(Kidhome), y = MntFishProducts, color = "Fish"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~") +
  stat_regline_equation(aes(x = factor(Kidhome), y = MntSweetProducts, color = "Sweet"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~") +
  stat_regline_equation(aes(x = factor(Kidhome), y = MntGoldProds, color = "Gold"), label.x.npc = "right", label.y.npc = 0.15, formula = y ~ x, size = 3, label.fontsize = 14, label.sep = " ~italic(\"*p=\"~")

```


```{r}
ggplot(data = Customer, aes(x = factor(Kidhome), y = MntWines, fill = factor(Kidhome))) +
  geom_boxplot() +
  stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               formula = y ~ x, label.x = "left", label.y = "top", parse = TRUE, size = 3) +
  geom_smooth(aes(group = 1), method = "lm", se = FALSE, color = "black", size = 0.7) +
  labs(x = "Number of Children in Household", y = "Amount Spent on Products") +
  scale_fill_discrete(name = "Number of Children") +
  theme(legend.position = "bottom")

```
















